A study of the effects of within functional group diversity on the response

### 2021-04-16 various_stuff/dev_vignettes/within-function-group-diversity.Rmd
fixed the n() error
by dplyr::filter , rather than just filter !!!!!!!!

```{r setup}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

@@

simulation_result <- run_simulation(dynamic_model = bushplus_dynamic_model_strains,
                                    parameter_values = one_strain_params,
                                    initial_state = one_strain_initial_state,
                                    event_definition = default_event_definition_strains)

>>>>

```{r setup}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE, cache = FALSE,
                      fig.align = "centre", fig.width = 7, fig.height = 7)

@@

simulation_result <- run_simulation(dynamic_model = bushplus_dynamic_model_strains,
                                    parameter_values = one_strain_params,
                                    initial_state = one_strain_initial_state,
                                    event_definition = default_event_definition_strains)
every_n <- 10
plot_dynamics_strains(simulation_result)
